Chemistry of fossil Pinus pollen and the effect of acetolysis

### 2021-05-18 manuscript.Rmd
wrote some on results

```{r}
readRDS(here("data","output","pca_plots.rds"))
readRDS(here("data","output","lda_tables.rds"))
```

@@

>>>>

i. Differences between cores
ii.i Difference between acetolysed and fossil
ii.ii Difference between fresh and fossil grains.
iii effect of depth/age on chemistry

There are differences between fresh and fossil grains.
Most notibly the lipid peak at 1745 is not visible in the fossil grains, neither acetolysed or raw fossil pollen.
Changes in the carbohydrate region from 1000 to 1250.
in SPT pollen there is a dominant peak there.
The most prominent and characteristic sporopollenin peaks are clearly visible in the fossil pollen, 1600, 1510 and 1170, while the rest of the spectra have changed substantially.

1170 is more pronounced in spt than acet

```{r message=FALSE, warning=FALSE, include=FALSE}
pca_acet_select = readRDS(here("data","output","pca_plots.rds"))
lda_tables = readRDS(here("data","output","lda_tables.rds"))
```

```{r pca_acet_sel echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "PCA all cores, only samples present in both acet and SPT"}
pca_acet_select[1]
```

@@

# Discussion
